\documentclass[12pt]{article}

% Basic setup
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{setspace}
\onehalfspacing

% Math and symbols
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}

% Graphics and tables
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}

% Bibliography and references
\usepackage[backend=biber,style=alphabetic,sorting=nyt]{biblatex}
\addbibresource{references.bib}

% Hyperlinks (load last)
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=red,
    urlcolor=blue
}

% Custom macros
\input{macros}

% Document information
\title{Research Paper Title}
\author{Author Name}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract of your research paper. Briefly describe the problem, methods, results, and conclusions. Keep it concise but informative, typically 150-250 words.
\end{abstract}

\tableofcontents
\newpage

% MODULAR SECTIONS - Edit individual files in sections/ directory
% This approach allows AI to focus on one section at a time

% Uncomment to use modular sections:
% \input{sections/introduction}
% \input{sections/methodology}
% \input{sections/results}
% \input{sections/discussion}
% \input{sections/conclusion}

% For now, using simplified inline sections for demonstration:

\section{Introduction}

This is the introduction section. Here you should:
\begin{itemize}
    \item Introduce the research problem
    \item Provide background and motivation
    \item State your contributions
    \item Outline the paper structure
\end{itemize}

You can use citations like this \cite{exampleref} and mathematical expressions like $f(x) = x^2 + 1$.

\section{Literature Review}

Discuss related work and how your research fits into the existing literature. Compare and contrast different approaches.

\section{Methodology}

Describe your research methods, experimental setup, or theoretical framework. Use mathematical notation when appropriate:

\begin{equation}
    \mathbb{E}[X] = \sum_{i=1}^{n} x_i P(X = x_i)
\end{equation}

You can also use the custom macros defined in `macros.tex`:
- Real numbers: $\R$
- Natural numbers: $\N$
- Argmax operator: $\argmax_{x} f(x)$

\section{Results}

Present your findings here. Include tables and figures as needed:

\begin{table}[h]
\centering
\begin{tabular}{@{}lcc@{}}
\toprule
Method & Accuracy & Runtime \\
\midrule
Algorithm A & 95.2\% & 10.3s \\
Algorithm B & 92.8\% & 5.7s \\
\bottomrule
\end{tabular}
\caption{Comparison of different algorithms}
\label{tab:results}
\end{table}

\section{Discussion}

Interpret your results, discuss limitations, and suggest future work. You can reference tables like Table~\ref{tab:results}.

\section{Conclusion}

Summarize your main findings and contributions. Restate the significance of your work.

% Examples of TODO and NOTE commands from macros.tex
\todo{Remember to add more experimental results}
\note{Consider discussing computational complexity}

\printbibliography

\end{document}